FinalManuscript_DISCS_UG

### 2019-04-09 parts/00_abstract.tex
Add chapter 4 contents

\begin{thesisabstract}
    \noindent
    Homomorphic cryptography allows for encrypted data to be modified and operated on without requiring decryption, although current homomorphic cryptosystems are either limited in their permitted operations or are significantly more time-intensive than standard non-homomorphic cryptosystems. Regardless, homomorphic cryptography has been targeted for use in secure image processing and facial recognition, due to their ability to maintain data privacy. In this paper, we compared the viability of the Paillier, Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK), and Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystems for facial image processing applications, by implementing a software library equipped with these cryptosystems, and comparing their time efficiency and accuracy. Furthermore, as an extension to previous research, we attempt to support non-linear image processing operations by deriving and implementing applicable closed-form approximations. Preliminary results have shown that the Paillier and DGK cryptosystems are comparable in accuracy and may be used for image negation, but only the Paillier cryptosystem is consistent enough to produce reasonable to accurate results.

>>>>

\begin{thesisabstract}
    \noindent
    Homomorphic cryptography allows for encrypted data to be modified and operated on without requiring decryption, although current homomorphic cryptosystems are either limited in their permitted operations or are significantly more time-intensive than standard non-homomorphic cryptosystems. Regardless, homomorphic cryptography has been targeted for use in secure image processing and facial recognition, due to their ability to maintain data privacy. In this paper, we compared the viability of the Paillier, Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK), Dijk--Gentry--Halevi--Vaikuntanathan (DGHV), and Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystems for facial image processing applications, by implementing a software library equipped with these cryptosystems, and comparing their time efficiency and accuracy. Furthermore, as an extension to previous research, we attempt to support non-linear image processing operations by deriving and implementing applicable closed-form approximations. Preliminary results have shown that the Paillier and DGK cryptosystems are comparable in accuracy and may be used for image negation, but only the Paillier cryptosystem is consistent enough to produce reasonable to accurate results.

### 2019-04-09 parts/00_acknowledgements.tex

    \noindent
    We would like to thank Dr. Ma. Mercedes Rodrigo, Dr. Ma. Regina Estuar, and Dr. Proceso Fernandez, Jr. for initiating the creation of this thesis template for use of undergraduate thesis groups for years to come. We also extend our gratitude to Ms. Jessica Sugay for help invaluable help in automating many of the formatting of this template, especially in the creation of the custom styles, table of contents, list of figures, list of tables, and the bibliography.

    This section, as the name suggests, is the place in your paper where you may acknowledge individuals or groups who, with their help or guidance, made your study feasible and ultimately a reality. Some of these people include your adviser, volunteers for your study, other professors who may have contributed to your study, and if applicable, any group or organization who provided support in any way for your research.

>>>>

    \noindent
    We would like to thank our adviser, Dr. William Emmanuel S. Yu, and our panelists Dr. Andrei D. Coronel and Dr. Mari-Jo P. Ruiz for lending their expertise and for giving their invaluable comments and insights.
Due acknowlegement is also given to the University of Essex for making the \texttt{faces94} dataset publicly available for research purposes.

    % We would like to thank Dr. Ma. Mercedes Rodrigo, Dr. Ma. Regina Estuar, and Dr. Proceso Fernandez, Jr. for initiating the creation of this thesis template for use of undergraduate thesis groups for years to come. We also extend our gratitude to Ms. Jessica Sugay for help invaluable help in automating many of the formatting of this template, especially in the creation of the custom styles, table of contents, list of figures, list of tables, and the bibliography.

    % This section, as the name suggests, is the place in your paper where you may acknowledge individuals or groups who, with their help or guidance, made your study feasible and ultimately a reality. Some of these people include your adviser, volunteers for your study, other professors who may have contributed to your study, and if applicable, any group or organization who provided support in any way for your research.

### 2019-04-09 parts/01_introduction_05scopeandlimitations.tex
Applied comments for chapter 1

\section{Scope and Limitations of the Study}
Our study will be limited in terms of the cryptosystems to be tested, the image processing operations we will implement, and the statistical tests we will use to gauge the security of the cryptosystems. Below is a listing of the scope of the study.

We will implement and test the following algorithms:
\begin{enumerate}
	\item A variant of the Paillier cryptosystem~\cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg}~\cite{ziad_cryptoimg:_2016}.
    \item The Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK) cryptosystem~\cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is primarily used for secure integer comparison.
	\item A fully homomorphic encryption scheme by Dasgupta and Pal, which uses polynomial rings~\cite{dasgupta_design_2016}.
	\item The Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystem \cite{cryptoeprint:2011:277}, an improvement on the lattice-based cryptosystem by Gentry~\cite{gentry_fully_2009}, with optimizations from Smart, Vercauteren and Halevi \cite{hutchison_fully_2010, cryptoeprint:2011:566}.
\end{enumerate}
We will implement and test the following categories of image manipulation operations:
\begin{enumerate}
	\item Non-linear image intensity adjustment (logarithm and power-log transformations)
	\item Facial detection and recognition using the eigenface approach \cite{turk_eigenfaces_1991}.
\end{enumerate}
We will adopt the benchmark for evaluating image quality of image encryption schemes presented by Ahmed, et. al~\cite{ahmed_benchmark_2016}. The presented benchmark reflects many tests used in other literature~\cite{ahmad_efficiency_2012, wu_npcr_2011}.
\begin{enumerate}
	%\item Tests for preservation of image quality after encryption and decryption
	%\begin{enumerate}
		\item Mean Squared Error (MSE)
		\item Peak Signal to Noise Ratio (PSNR)
		\item Structural Similarity Index (SSIM)
	%\end{enumerate}
	%\item Tests for cryptographic security
	%\begin{enumerate}
	%	\item Information entropy analysis
	%	\item Correlation coefficient analysis
	%	\item Differential analysis
  %      \begin{enumerate}
  %          \item Number of Pixel Change Rate (NPCR)
  %          \item Universal Average Change Intensity (UACI)
  %      \end{enumerate}
	%\end{enumerate}
\end{enumerate}
A detailed overview of the above will be provided in the methodology. Grayscale images will be used in the study.
A client-server model for secure computation will be assumed to allow operations such as secure comparison and exponentiation.

>>>>

\section{Scope and Limitations of the Study}
Our study will test a fixed set of cryptosystems and image processing operations. 
We will implement and test the following algorithms:
\begin{enumerate}
	\item A variant of the Paillier cryptosystem~\cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg}~\cite{ziad_cryptoimg:_2016}.
  \item The Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK) cryptosystem~\cite{pieprzyk_efficient_2007, cryptoeprint:2008:321}.
	\item The DGHV cryptosystem by Dijk, Gentry, Halevi, and Vaikuntanathan \cite{cryptoeprint:2009:616}, with optimizations from Coron, Naccache, and Tibouchi, \cite{cryptoeprint:2011:277, cryptoeprint:2011:440} to support shorter public keys.
	\item The Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystem \cite{cryptoeprint:2011:277}, an improvement on the lattice-based cryptosystem by Gentry~\cite{gentry_fully_2009}, with optimizations from Smart, Vercauteren and Halevi \cite{hutchison_fully_2010, cryptoeprint:2011:566}.
\end{enumerate}
We will implement and test the following categories of image manipulation operations:
\begin{enumerate}
	\item Non-linear intensity adjustment (logarithm, power-log transformations)
	\item Facial detection and recognition using the eigenface approach \cite{turk_eigenfaces_1991}.
\end{enumerate}
To test for image quality, we will adopt the benchmark for evaluating image quality of image encryption schemes presented by Ahmed, et. al~\cite{ahmed_benchmark_2016}. The presented benchmark uses many tests used in other literature~\cite{ahmad_efficiency_2012, wu_npcr_2011}.
\begin{enumerate}
	%\item Tests for preservation of image quality after encryption and decryption
	%\begin{enumerate}
		\item Mean Squared Error (MSE)
		\item Peak Signal to Noise Ratio (PSNR)
		\item Structural Similarity Index (SSIM)
	%\end{enumerate}
	%\item Tests for cryptographic security
	%\begin{enumerate}
	%	\item Information entropy analysis
	%	\item Correlation coefficient analysis
	%	\item Differential analysis
  %      \begin{enumerate}
  %          \item Number of Pixel Change Rate (NPCR)
  %          \item Universal Average Change Intensity (UACI)
  %      \end{enumerate}
	%\end{enumerate}
\end{enumerate}
A detailed overview of the above will be provided in the methodology. Grayscale images will be used in the study.
A client-server model for secure computation will be assumed to allow operations such as secure comparison and exponentiation.
Training and test data are taken from the publicly available \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.

### 2019-04-09 parts/02_relatedliterature.tex

We have presented as well several areas in which our study will expand on the research so far.
\begin{enumerate}
  \item We have shown two fully homomorphic cryptosystems, the Dasgupta-Pal cryptosystem and the BGV cryptosystem. While these cryptosystems are generally less efficient than partially homomorphic cryptosystems, they do not require additional protocols for exponentiation.
  \item Due to the general limitations of partially homomorphic systems, attempts at applying homomorphic cryptography to applications such as image processing and facial recognition have mainly been restricted to linear operations on ciphertext. We have shown that there are basic image processing operations which are non-linear, which we can implement.
  \item While privacy-preserving facial recognition has been accomplished by Erkin, et al., privacy-preserving facial detection is an area of research which has yet to explored.
\end{enumerate}

>>>>

We have presented as well several areas in which our study will expand on the research so far.
\begin{enumerate}
  \item We have shown two fully homomorphic cryptosystems, the Dasgupta-Pal cryptosystem and the BGV cryptosystem. While these cryptosystems are generally less efficient than partially homomorphic cryptosystems, they do not require additional protocols for exponentiation.
  \item Due to the general limitations of partially homomorphic systems, attempts at applying homomorphic cryptography to applications such as image processing and facial recognition have mainly been restricted to linear operations on ciphertext. We have shown that there are basic image processing operations which are non-linear, which we can implement.
  \item While privacy-preserving facial recognition has been accomplished by Erkin, et al., privacy-preserving facial detection has yet to explored.
\end{enumerate}

### 2019-04-09 parts/02_relatedliterature_02commonimageprocessingoperations.tex
final final final
final final final

\section{Image Intensity Transformations}
We represent a digital image $R$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$. We use $R(x,y)$ represents the entry at the $x$th row and $y$th column of a matrix $R$.
An intensity transformation on an image $R$ can be defined as a function $T$ which maps a pixel value $r$ to a new value $r^\prime$, which we can write as $r^\prime = T\left(r\right)$. This function is then applied to every pixel in $R$.
The \textit{CryptoImg} library implemented two types of linear intensity transformations: image negation and brightness control.

@@

\begin{comment}
\subsection{Spatial Filtering}
The \textit{CryptoImg} library also implemented \textit{spatial filters}. Spatial filters are operators which determine output pixels using information from neighboring input pixels. To apply a spatial filter to obtain a resulting image $R^\prime$, a convolution is performed between an $m \times n$ matrix $k$, called a kernel, and the original $M\times N$ image $R$.
A convolution between a kernel $k$ and image $R$ which yields a resulting image $R^\prime$, denoted as $R^\prime = k \ast R$, is defined by
\begin{align} \label{eq:spatialfilter}
	R^\prime(x,y) = \sum_{s=1}^m{\sum_{t=1}^n{k(s,t)R(x+s,y+t)}}, \text{ for all } 0\leq x \leq M, 0 \leq y \leq N,
\end{align}

\begin{figure*}[!ht]
    \centering
    \includegraphics[width=\textwidth,\keepaspectratio]{Figures/SpatialFilter.png}
    \caption{A sample image $R$ and sample kernel $k$.}
    \label{fig:spatialfilter}
\end{figure*}
For example, using the image and $3 \times 3$ kernel given in Figure \ref{fig:spatialfilter}, we can calculate the value in the third row and fourth column of the resulting image $R^\prime$ by adding the products of entries in $k$ with the corresponding entries in $R$, found in an $3 \times 3$ region around $R(3,4)$.
\begin{align*}
	R^\prime(3,4) &= \sum_{s=1}^m{\sum_{t=1}^n{k(s,t)R(3+s,4+t)}}\\
	&= (0.0625\times 200) + (0.1250\times 249) + (0.0625\times 255) \\
	&+ (0.1250\times 143) + (0.2500\times 223) + (0.1250\times 255) \\
	&+ (0.0625\times 196) + (0.1250\times 236) + (0.0625\times 255)\\
	&= 223.
\end{align*}
Since spatial filters take values from a contiguous region of pixels, this presents a difficulty in homomorphic cryptosystems: in order for spatial filters to be performed, the location of each pixel relative to neighboring pixels has to be preserved. This was performed in the implementation of spatial filters in the \textit{CryptoImg} library~\cite{ziad_cryptoimg:_2016}. We wish to implement spatial filters using a similar approach, and assess how preserving spatial correlation between pixels can impact the security of the encrypted image.

\subsection{Common Spatial Filtering Kernels}
Edge detection is used to find and determine the boundaries in an image, commonly used in applications such as image segmentation and feature extraction. This works by detecting so-called \textit{edges}, areas that have abrupt changes in intensity.
One common method of performing edge detection is the Sobel operator, which uses two spatial filters to approximate the gradient of an image. Given an image $R$, and the kernels
\begin{equation}
    g_x =
    \begin{bmatrix}
        -1 & 0 & 1 \\
        -2 & 0 & 2 \\
        -1 & 0 & 1
    \end{bmatrix}
    \qquad\text{and}\qquad
    g_y =
    \begin{bmatrix}
        1 & 2 & 1 \\
        0 & 0 & 0 \\
        -1 & -2 & -1
    \end{bmatrix},
\end{equation}
$g_x \ast R$ yields the horizontal component of the gradient, while $g_y \ast R$ yields the vertical component of the gradient.

There are also spatial filters that perform image smoothing (such as Gaussian blur and box blur, which use the kernels $b_g$ and $b$ respectively in Equation~\ref{eqn:smooth-filters}) and image sharpening~\cite{gonzalez_digital_2008}.
\begin{equation}
    \label{eqn:smooth-filters}
    b_g = \frac{1}{16}
    \begin{bmatrix}
        1 & 2 & 1 \\
        2 & 4 & 2 \\
        1 & 2 & 1
    \end{bmatrix}
    \qquad
    b = \frac{1}{9}
    \begin{bmatrix}
        1 & 1 & 1 \\
        1 & 1 & 1 \\
        1 & 1 & 1
    \end{bmatrix}
\end{equation}

%% TODO: specific list of kernels to use for this study
\end{comment}

>>>>

\section{Image Intensity Transformations}
We represent a digital image $R$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$. We use $R(x,y)$ to represent the entry at the $x$th row and $y$th column of a matrix $R$.
An intensity transformation on an image $R$ can be defined as a function $T$ which maps a pixel value $r$ to a new value $r^\prime$, which we can write as $r^\prime = T\left(r\right)$. This function is then applied to every pixel in $R$.
The \textit{CryptoImg} library implemented two types of linear intensity transformations: image negation and brightness control.

@@

% \subsection{Spatial Filtering}
% The \textit{CryptoImg} library also implemented \textit{spatial filters}. Spatial filters are operators which determine output pixels using information from neighboring input pixels. To apply a spatial filter to obtain a resulting image $R^\prime$, a convolution is performed between an $m \times n$ matrix $k$, called a kernel, and the original $M\times N$ image $R$.
% A convolution between a kernel $k$ and image $R$ which yields a resulting image $R^\prime$, denoted as $R^\prime = k \ast R$, is defined by
% \begin{align} \label{eq:spatialfilter}
% 	R^\prime(x,y) = \sum_{s=1}^m{\sum_{t=1}^n{k(s,t)R(x+s,y+t)}}, \text{ for all } 0\leq x \leq M, 0 \leq y \leq N,
% \end{align}

% \begin{figure*}[!ht]
%     \centering
%     \includegraphics[width=\textwidth,\keepaspectratio]{Figures/SpatialFilter.png}
%     \caption{A sample image $R$ and sample kernel $k$.}
%     \label{fig:spatialfilter}
% \end{figure*}
% For example, using the image and $3 \times 3$ kernel given in Figure \ref{fig:spatialfilter}, we can calculate the value in the third row and fourth column of the resulting image $R^\prime$ by adding the products of entries in $k$ with the corresponding entries in $R$, found in an $3 \times 3$ region around $R(3,4)$.
% \begin{align*}
% 	R^\prime(3,4) &= \sum_{s=1}^m{\sum_{t=1}^n{k(s,t)R(3+s,4+t)}}\\
% 	&= (0.0625\times 200) + (0.1250\times 249) + (0.0625\times 255) \\
% 	&+ (0.1250\times 143) + (0.2500\times 223) + (0.1250\times 255) \\
% 	&+ (0.0625\times 196) + (0.1250\times 236) + (0.0625\times 255)\\
% 	&= 223.
% \end{align*}
% Since spatial filters take values from a contiguous region of pixels, this presents a difficulty in homomorphic cryptosystems: in order for spatial filters to be performed, the location of each pixel relative to neighboring pixels has to be preserved. This was performed in the implementation of spatial filters in the \textit{CryptoImg} library~\cite{ziad_cryptoimg:_2016}. We wish to implement spatial filters using a similar approach, and assess how preserving spatial correlation between pixels can impact the security of the encrypted image.

% \subsection{Common Spatial Filtering Kernels}
% Edge detection is used to find and determine the boundaries in an image, commonly used in applications such as image segmentation and feature extraction. This works by detecting so-called \textit{edges}, areas that have abrupt changes in intensity.
% One common method of performing edge detection is the Sobel operator, which uses two spatial filters to approximate the gradient of an image. Given an image $R$, and the kernels
% \begin{equation}
%     g_x =
%     \begin{bmatrix}
%         -1 & 0 & 1 \\
%         -2 & 0 & 2 \\
%         -1 & 0 & 1
%     \end{bmatrix}
%     \qquad\text{and}\qquad
%     g_y =
%     \begin{bmatrix}
%         1 & 2 & 1 \\
%         0 & 0 & 0 \\
%         -1 & -2 & -1
%     \end{bmatrix},
% \end{equation}
% $g_x \ast R$ yields the horizontal component of the gradient, while $g_y \ast R$ yields the vertical component of the gradient.

% There are also spatial filters that perform image smoothing (such as Gaussian blur and box blur, which use the kernels $b_g$ and $b$ respectively in Equation~\ref{eqn:smooth-filters}) and image sharpening~\cite{gonzalez_digital_2008}.
% \begin{equation}
%     \label{eqn:smooth-filters}
%     b_g = \frac{1}{16}
%     \begin{bmatrix}
%         1 & 2 & 1 \\
%         2 & 4 & 2 \\
%         1 & 2 & 1
%     \end{bmatrix}
%     \qquad
%     b = \frac{1}{9}
%     \begin{bmatrix}
%         1 & 1 & 1 \\
%         1 & 1 & 1 \\
%         1 & 1 & 1
%     \end{bmatrix}
% \end{equation}

%% TODO: specific list of kernels to use for this study

### 2019-04-09 parts/02_relatedliterature_05partiallyhomomorphic.tex

In this section, we will present two classical partially homomorphic encryption (PHE) schemes which we will be testing in the study: the Paillier cryptosystem and the DGK cryptosystem. Both of these cryptosystems encrypt integer plaintexts and are additively homomorphic and allow for the multiplication of a plaintext scalar. We will then show how these PHE schemes may be adapted for secure floating-point computation.

@@

As the multiplicative homomorphism was not presented in the original paper, we provide a short proof here.
\begin{proof}
  Let $m \in \mathbb{Z}_u$ and $k\in \mathbb{N}$.
  We consider $E(m)^k = (g^m \cdot h^r \bmod{n})^k\bmod n$.
  \begin{align*}
    (g^m \cdot h^r \bmod{n})^k \bmod n
    &= (g^m \cdot h^r)^k \bmod{n}\\
    &= (g^m)^k \cdot (h^r)^k \bmod{n}\\
    &= g^{km} \cdot (h^{kr}) \bmod{n}
  \end{align*}
  Since $r$ is a random integer, $kr$ is also a random integer, Therefore, $g^{km} \cdot (h^{kr}) \bmod{n} = D(E(m)^k)$ is a valid encryption of the message $km$.
\end{proof}

\subsection{Floating-Point Arithmetic using PHE}
\label{sec:fp_arithmetic}
We have discussed the Paillier and DGK cryptosystems, which encrypt and allow similar operations on encrypted integers. We will now show how these PHE schemes may be extended to a system which allows for secure floating-point computation.

In this section, we let $\oplus$ and $\otimes$ represent the homomorphic operations which correspond to the addition and multiplication of integers in a PHE scheme, respectively.

\subsubsection{Extension to Floating-Point Numbers}
\label{sec:fp_operations}
We can use the following protocol described in~\cite{ziad_cryptoimg:_2016} in order to extend Paillier and DGK to floating-point numbers.

@@

By applying these extensions to the Paillier and DGK cryptosystems, privacy-preserving floating-point arithmetic can be acheived.

>>>>

In this section, we will present two classical partially homomorphic encryption (PHE) schemes which we will be testing in the study: the Paillier cryptosystem and the DGK cryptosystem. Both of these cryptosystems encrypt integer plaintexts, are additively homomorphic, and allow for the multiplication of a plaintext scalar. We will then show how these PHE schemes may be adapted for secure floating-point computation using two-party protocols.

@@

As the multiplicative homomorphism was not presented in the original paper \cite{pieprzyk_efficient_2007, cryptoeprint:2008:321}, we provide a short proof here.
\begin{proof}
  Let $m \in \mathbb{Z}_u$ and $k\in \mathbb{N}$.
  We consider $E(m)^k = (g^m \cdot h^r \bmod{n})^k\bmod n$.
  \begin{align*}
    (g^m \cdot h^r \bmod{n})^k \bmod n
    &= (g^m \cdot h^r)^k \bmod{n}\\
    &= (g^m)^k \cdot (h^r)^k \bmod{n}\\
    &= g^{km} \cdot (h^{kr}) \bmod{n}
  \end{align*}
  Since $r$ is a random integer, $kr$ is also a random integer, Therefore, $g^{km} \cdot (h^{kr}) \bmod{n} = E(m)^k$ is a valid encryption of the message $km$.
\end{proof}

\subsection{Floating-Point Arithmetic using PHE}
\label{sec:fp_arithmetic}
We have discussed the Paillier and DGK cryptosystems, which encrypt and allow similar operations on encrypted integers. We will now show how these PHE schemes may be extended to a system which allows for secure floating-point computation. In this section, we let $\oplus$ and $\otimes$ represent the homomorphic operations corresponding to the addition and multiplication of integers in a PHE scheme, respectively.

\subsubsection{Extension to Floating-Point Numbers}
\label{sec:fp_number_extension}
We can use the following protocol, described in~\cite{ziad_cryptoimg:_2016}, in order to extend Paillier and DGK to floating-point numbers.

@@

By applying these extensions to the Paillier and DGK cryptosystems, privacy-preserving floating-point arithmetic can be acheived with PHE schemes.

### 2019-04-09 parts/03_methodology.tex
Add citation for scikit-image
Misc edits (Ch2,3,appendix,abstract, acknowledgements)

In this study we apply four homomorphic encryption schemes~\cite{ziad_cryptoimg:_2016, pieprzyk_efficient_2007, dasgupta_design_2016, garay_algorithms_2014} for use in image processing and facial recognition applications.
While the Paillier and DGK cryptosystems have been implemented for use in image processing in~\cite{ziad_cryptoimg:_2016, hutchison_privacy-preserving_2009}, the other cryptosystems have to be adapted for this study.
Two experiments were conducted in this study:
\begin{enumerate}
	\item Assessment of non-linear image intensity transformations under each of the four cryptosystems.
	\item Assessment of efficiency of each of the four cryptosystems when applied for use in privacy-preserving facial recognition and detection using eigenfaces.
\end{enumerate}
The results of the image intensity transformations were tested for image quality using benchmarks in~\cite{ahmed_benchmark_2016}.

\section{Cryptosystem Implementation}

% The current version of the OpenCV library (3.4.2) will be forked from the open-source GitHub repository at \url{https://github.com/opencv/opencv})~\cite{bradski_opencv_2000}.

Four homomorphic encryption schemes were investigated. For cryptosystems with readily available open-source implementations, such implementations were used. For the remaining cryptosystems, the encryption and decryption methods were implemented in Python.
\begin{itemize}
	\item The Paillier cryptosystem was incorporated using the implementation at \url{https://github.com/n1analytics/python-paillier} developed by Data61 - CSIRO.
	\item The BGV cryptosystem was implemented using the Pyfhel library (\url{https://github.com/ibarrond/Pyfhel}) using a HElib backend from (\url{https://github.com/shaih/HElib}).
	\item The DGK and Dasgupta--Pal cryptosystem were implemented from scratch.
\end{itemize}

@@

\input{parts/03_methodology_01integertorealnumbers}
\input{parts/03_methodology_02nonlinearintensitytransformations}

@@

Lab computers in Faura Hall, Ateneo de Manila University were used to perform the computations, and processing time was tracked using built-in timing functions. The processing time for all cases were recorded.

@@

We first obtained standard test images from~\cite{gonzalez_image_nodate}. Grayscale images were used in the study.

@@

\subsection{Facial Recognition Tests}
%% TODO: Brian, can you fill this part up? Yes
The method for secure facial recognition using eigenfaces by Erkin, et al. \cite{hutchison_privacy-preserving_2009-2} was implemented for this study.
%Training data will be secured from The Database of Faces (\url{https://www.cl.cam.ac.uk/research/dtg/attarchive/facedatabase.html}) maintained by AT&T Laboratories Cambridge.
Training and test data were secured from the \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.

@@

\section{Summary}
In summary, the study consists of:
\begin{itemize}
	\item Creating a wrapper library that acts as a unified interface which implements the Paillier, DGK, Dasgupta--Pal, and BGV homomorphic cryptosystems.
	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.
	\item Conducting tests for image quality, processing time, using standard test images from~\cite{gonzalez_image_nodate}.
\end{itemize}

%% insert flowchart/diagrams here

>>>>

In this study we apply four homomorphic encryption schemes~\cite{ziad_cryptoimg:_2016, pieprzyk_efficient_2007, dasgupta_design_2016, garay_algorithms_2014} for use in image processing and facial recognition applications.
While the Paillier and DGK cryptosystems have been implemented for use in image processing in~\cite{ziad_cryptoimg:_2016, hutchison_privacy-preserving_2009}, the other cryptosystems have to be adapted for this study.
Two experiments were conducted in this study:
\begin{enumerate}
	\item Assessment of non-linear image intensity transformations under each of the four cryptosystems.
	\item Assessment of efficiency of each of the four cryptosystems when applied for use in privacy-preserving facial recognition and detection using eigenfaces.
\end{enumerate}
% redundant sentence, this is explained later:
% The results of the image intensity transformations were tested for image quality using benchmarks in~\cite{ahmed_benchmark_2016}.

\section{Cryptosystem Implementation}
% The current version of the OpenCV library (3.4.2) will be forked from the open-source GitHub repository at \url{https://github.com/opencv/opencv})~\cite{bradski_opencv_2000}.

Four homomorphic encryption schemes were investigated. For cryptosystems with readily available open-source implementations, such implementations were used. For the remaining cryptosystems, the encryption and decryption methods were implemented in Python.
\begin{itemize}
	\item The Paillier cryptosystem is incorporated using the \texttt{python-paillier} library at \url{https://github.com/n1analytics/python-paillier} developed by Data61 - CSIRO.
	\item The DGK cryptosystem is ported from the C++ implementation at \url{https://github.com/encryptogroup/ENCRYPTO_utils}, developed by Daniel Demmler from EC-SPRIDE.
	\item The DGHV cryptosystem is ported from the C++ implementation at 
	\url{https://github.com/deevashwer/Fully-Homomorphic-DGHV-and-Variants}.
	\item The BGV cryptosystem is implemented using the Pyfhel library (\url{https://github.com/ibarrond/Pyfhel}) using a HElib backend from (\url{https://github.com/shaih/HElib}).
\end{itemize}

@@

The Paillier and DGK cryptosystems were adapted for floating-point computations using the protocols described in section \ref{sec:fp_arithmetic}.

\input{parts/03_methodology_02nonlinearintensitytransformations}

@@

A laptop computer with a 2.5 GHz Intel Core i7 quad-core processor and 8 GB of RAM is used to perform the computations, and processing time was tracked using built-in timing functions. The processing time for all cases were recorded. All of the tests are done using Python 3.7.1 running on Linux.

@@

We first obtained test images from the \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex. However, only ten distinct facial images from the dataset were selected for the purposes of this test. Since only grayscale images are used in the study, the images were converted to grayscale and then downsampled to $40 \times 36$ pixels.

For each cryptosystem, three image operations are tested:
\begin{enumerate}
	\item Image negation
	\item Logarithm transformation, with $c = 30$
	\item Power-law transformation, with $c = 1$ and $\gamma = 0.4$
\end{enumerate}

@@

Computing for MSE, PSNR, and SSIM was done using the corresponding built-in functions from the scikit-image Python library \cite{scikit-image}.

\subsection{Facial Recognition Tests}
%% TODO: Brian, can you fill this part up? Yes. OK Thanks
The method for secure facial recognition using eigenfaces by Erkin, et al. \cite{hutchison_privacy-preserving_2009-2} was implemented for this study.
%Training data will be secured from The Database of Faces (\url{https://www.cl.cam.ac.uk/research/dtg/attarchive/facedatabase.html}) maintained by AT&T Laboratories Cambridge.
Training and test data were secured from the \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.

@@

% \section{Summary}
% In summary, the study consists of:
% \begin{itemize}
% 	\item Creating a wrapper library that acts as a unified interface which implements the Paillier, DGK, DGHV, and BGV homomorphic cryptosystems.
% 	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.
% 	\item Conducting tests for image quality, processing time, using standard test images from~\cite{gonzalez_image_nodate}.
% \end{itemize}

%% insert flowchart/diagrams here
% sure
